Algorithmic and Economic Aspects of the Internet

### 2012-12-03 report/paper.tex
Added less bidding explanation.

\subsubsection{1 v. 1} No trading occurs in this experiment. In figures 2 and 3,
you can see the shouts made by the bots. The Shaver buyer and seller traders
tend toward the equilibrium price over time but don't manage to reach it before
the market session ends. The AA bot makes very few trades and is always out-bid
/ out-asked by Shaver.

@@

\subsubsection{1 v. Many} In these experiments, trading starts at around round
90. In figures 4 and 5, we see that the Shaver bots tend towards the
equilibrium much faster than when there was only one bot; this is likely due to
there being 10 Shaver bots which are all trying to out-bid each other. When the
bids and asks converge, the Shaver bots invariably trade with themselves. Our
AA implementation is excluded from trading as it can't adjust its
aggressiveness quickly enough. Not all Shaver bots are engaged in making actual
trades at all times, the horizontal lines of bids / asks on the graphs indicate
that a Shaver bot is placing shouts at its limit price.

@@

Our implementation also seems to issue significantly fewer trades than would be
expected
--luke expand this

>>>>

\subsubsection{1 v. 1} No trading occurs in this experiment. In figures 2 and 3,
you can see the shouts made by the bots. The Shaver buyer and seller traders
tend toward the equilibrium price over time but don't manage to reach it before
the market session ends. The AA bot makes very few shouts and is always out-bid
/ out-asked by Shaver.

@@

\subsubsection{1 v. Many} With more Shaver bots, trading starts at around round
90. In figures 4 and 5, we see that the Shaver bots tend towards the
equilibrium as before but at a much faster rate than when there was only one
bot; this is likely due to there being 10 Shaver bots which are all trying to
out-bid each other. When the bids and asks converge, the Shaver bots invariably
trade with themselves. Our AA implementation is excluded from trading as it
can't adjust its aggressiveness quickly enough. Not all Shaver bots are engaged
in making actual trades at all times, the horizontal lines of bids / asks on the
graphs indicate that a Shaver bot is placing shouts at its limit price.

@@

Our implementation also seems to issue significantly fewer trades than would be
expected. Looking at the implemeentations of the other bots provided by D.
Cliff, it is not hard to see why. The implementations provided will always
return a trade when the bot has an order to fulfil (with the exception of the
Sniper bot which will make a shout on every round after a give threshold)
meaning these implementations have many more shouts on which to make profit.

This is contrary to our AA implementation which will not return a trade in the
case where the best bid in the market is greater than (for a buyer), or where
the best ask is less than (for a seller), the bot's limit price. This results
in our AA implementation not sharing it's information with the market which
would prevent other bots making offers that are more favourable to our AA bot.

\begin{enumerate}
\item
